---
title: "Social Media and Teens"
author: "Caroline Alexander and Elizabeth Slade"
format: revealjs
editor_options: 
  chunk_output_type: console
---

```{r}
# include: FALSE

library(tidyverse)
library(tinytable)
YRBS <- read_csv( "yrbs.csv" )
```

## Introduction

- What are we researching?
- What are the positive effects of social media?
- What are the negative effects of social media?

## How often do you use social media?

```{r}
# make your bar chart here
social_media <- YRBS |>
  select( q80 ) |>
  drop_na( q80 ) |> 
  mutate( q80 = as.character(q80) ) |> 
  mutate( q80 = case_when( q80 == "1" ~ "I do not use social media",
                           q80 == "2" ~ "A few times a month", q80 == "3" ~ "About once a week", q80 == "4" ~ "A few times a week", q80 == "5" ~ "About once a day", q80 == "6" ~ "Several times a day", q80 == "7" ~ "About once an hour", q80 == "8" ~ "More than once an hour" )) |>
  mutate( q80 = factor( q80, 
                        levels = c( "I do not use social media", "A few times a month", "About once a week", "A few times a week", "About once a day", "Several times a day", "About once an hour", "More than once an hour")))

ggplot(social_media) +
  geom_bar(aes( q80 )) +
  coord_flip() +
  labs( x = " ", y = "Number of Responses")

```

## How often do you use social media?

```{r}

social_media |>
  group_by( q80 ) |>
  count( name = "N" ) |>
  mutate( Total = nrow( social_media ), 
          Percent = 100*N/Total ) |>
  rename( " " = q80 ) |>
  tt( digits = 3 )

```


## During the past 12 months, have you ever been electronically bullied? 

```{r}
# make your bar chart here 
ggplot(YRBS) +
  geom_bar(aes( q25 )) +
  coord_flip() +
  labs( x = "Yes                                                No", y = "Number of Responses")
```

## Cyber bullying in the US

```{r}
state_data <- read_csv( "YRBS_All_Locations_Table.csv")
```

```{r}
library( sf )
library( geodata )
library( tmap )

tmap_options( basemap.server = "OpenStreetMap")
tmap_mode("plot")

us <- gadm( "USA", level = 1, path = getwd() )
us <- st_as_sf( us ) |>
  filter( NAME_1 != "Alaska", NAME_1 != "Hawaii" )

us <- left_join( us, 
                 state_data |>
                   filter( Stratification == "Total", Survey == "State" ) |>
                   rename( NAME_1 =  LocationDesc) |> 
                   select( NAME_1, Total = DataValue )) |>
  left_join( state_data |>
                   filter( Stratification == "Male", Survey == "State" ) |>
                   rename( NAME_1 =  LocationDesc) |> 
                   select( NAME_1, Male = DataValue ) ) |>
  left_join( state_data |>
                   filter( Stratification == "Female", Survey == "State" ) |>
                   rename( NAME_1 =  LocationDesc) |> 
                   select( NAME_1, Female = DataValue ) )

tm_shape( us ) +
  tm_polygons( id = "NAME_1", 
               fill = "Total", 
               fill.scale = tm_scale_intervals( n = 5, style = "jenks" ) )

tm_shape( us ) +
  tm_polygons( id = "NAME_1",
               fill = c("Female","Male"),
               fill.scale = tm_scale_intervals( n = 5, style = "jenks" ) )
```

## Conclusion 
- There is a lower cyber bullying rate than expected 
- If we were to continue our research we would want to look into what can be done to prevent cyber bullying
- As social media gets normalized for younger and younger kids its important to continue to monitor these stats. 



